---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#load libraries
library(tidyverse)
library(tidytext)
library(scales)
library(textdata)
library(data.table)
library(plotly)

#Read in data
sotu <- fread("sotu_final2.csv")

#load in word lists
source("WordLists.R")

#tokenise dataframe
singleword <- sotu %>% 
  unnest_tokens(word, text) %>%
  select(president, year, party, speech_type, word)

#remove stop words
sw_nostop <- singleword %>% 
  anti_join(stop_words) %>%
  anti_join(my_stop_words) %>% 
  anti_join(common_words)



```

## Analysis of the State of the Union Addresses

A State of the Union Address is mandated by Article II, Section 3 of the U.S. Constitution. It is through State of the Union  where the President and the Executive Branch is able to lay out their policy focus and try to recommend, or really push, Congress to go in certain policy directions.

Over time these addresses have substantially changed. The first several State of the Unions by George Washington and John Adams were speeches to Congress. Thomas Jefferson, however, began a 100 year tradition of giving written addresses. Jefferson felt that the practice needed to be changed to written because the oral presentation was too similar to the British Monarch practice of addressing new parliament with policy mandates rather than policy recommendations. In 1913 Woodrow Wilson changed it back to an oral presentation to Congress, which has remained the norm ever since. 

There are obvious major differences in tone, content, and standard of language when something is written versus something that is spoken. These differences are shown in the data, with written speeches being on average XXX words and spoken speeches being on average of XXX words. The longest speech was XXX in XXX at XXX words and the shortest speech was XXXX words by XXX in XXXX. 


## Getting the Data

All of the the data was scraped from XXX website, where I was able to develop a dataset with each SOTU speech and all the necessary metadata, such as president name, year of the address, and the political party of the president. 

![sotu page] (\img\posts\SOTU\SOTUwebpage.png)

I then was able to analyze the data from several different viewpoints. This analysis mostly covers 1-gram and bigram tokens, meaning that each row in the data was either a single word or a pair of words. Such a format allows us to analyze word frequencies, and word usage over time, among other things

```{r head, echo=F, message=F, warning=F}
head(sw_nostop)
```



## Some Mildly Interesting Facts about SOTU Addresses

What are the most common words, on average per speech (ordered boxplot) broken out by speech and written (frequencies will be very different based on massive difference in length of addresses)


tf-idf by president - lets show last 6 presidents, but lets see if we can build interactive tool, that would be super cool to show the top 15 words by tf-idf for whatever chosen president

![top 15 most common]()

![top 10 by last 6 presidents]()

![top 20 by party]()



## So how has the State of Black Americans been discussed in SOTUs?

Activism leads to being talked about -> leads to getting attention of leaders -> leads to being discussed by leaders -> leads to policy decisions and attention to targeted policy -> end note = activism matters, awareness matters, silence matters
silence = less policy focus

Point out how black people have been discussed. when discussed, is it actually for the benefit of them? Pull out the excerpt from abraham lincoln - even in a time when black people are fighting for freedom, lincoln spends XX lines on bargaining and pursuading white people that they will be okay when black people are free.

most discussions about black people has not been around the livelihood of black folk. It's been around the white elites and making sure they are happy or talking directly to them.

```{r black common 1-grams}
black_terms

```

![black terms over time]()

![most used black terms]()

